---
title: "P8105 HW 1"
author: "AJ Catalano"
date: "29 October 2021"
output: github_document
---

# Problem 1

Creating a data frame comprised of:

* a random sample of size 10 from a standard Normal distribution
* a logical vector indicating whether elements of the sample are greater than 0
* a character vector of length 10
* a factor vector of length 10, with 3 different factor “levels”

```{r}
# loading tidyverse
library(tidyverse)

# creating the data frame from above using tibble
df_1 = tibble(
  num_vec = rnorm(10),
  logic_vec = num_vec > 0,
  char_vec = c("Techno", "is", "superior", "to", "all", "other",
                "forms", "of", "electronic", "music"),
  factor_vec = factor(c("Acid", "Dub", "Dub", "Minimal", "Acid",
                         "Acid", "Minimal", "Dub", "Acid", "Minimal"))
)

df_1
```
df_1 is cool. If you cannot tell, I enjoy techno, which happens to be one of New York's only
redeeming offerings.

```{r, eval = FALSE}
mean(num_vec, logic_vec, char_vec, factor_vec)
```
When I try to take the mean of each variable using the above code, I am told that the first variable, num_vec, does not exist/is not found. I will try using the **pull** function.

```{r, collapse = TRUE}
# using the pull function to extract variables from df_1 and find their means
mean(df_1 %>% pull(num_vec))
mean(df_1 %>% pull(logic_vec))
mean(df_1 %>% pull(char_vec))
mean(df_1 %>% pull (factor_vec))
```
Using the above code, R returned numeric values for num_vec (`r mean(df_1 %>% pull(num_vec))`) and logic_vec (`r mean(df_1 %>% pull(logic_vec))`), but returned NA for char_vec and factor_vec.

```{r, eval = FALSE}
as.numeric(df_1 %>% pull(logic_vec))
as.numeric(df_1 %>% pull(char_vec))
as.numeric(df_1 %>% pull(factor_vec))
```
The **as.numeric** function returns integers for logic_vec and factor_vec, which means that R treats these vectors as numeric. However, the function returns NA for char_vec, showing that R does not treat character vectors as numeric.